Democratizing Secure Two-Party Computation

### 2017-10-13 OaklandSubmission/intro.tex
reference

\noindent\textbf{Other Related Work} 
Before ABY \cite{aby}, to improve efficiency, several works proposed
to mix secure computation protocols based on homomorphic
encryption with Yao’s garbled circuits protocol, e.g., \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,shropfer11}
  and developed tools that allowed writing a mixed SMC protocol, e.g., \cite{bogdanov,lone,tasty}. The assignment can
even be done automatically as was shown in \cite{autoS}. 
However, as noted by ABY, due to high conversion cost between homomorphic encryption and Yao's garbled circuit, these mixed protocols do not gain much over single protocol. Also, none of these works give a high-level developer-friendly language support.
No prior work has given a formal type system and operational semantics for mixed arithmetic and boolean back-ends.
In our evaluation, we use benchmarks for the problem of secure prediction where the cloud holds the secret model and the client holds the secret input. For this problem various works have considered tailor-made protocols depending on the model considered \cite{shafindss,wu,secureml,minionn}. In our evaluation, we compare our performance with these specialized protocols and give competitive run-times. We provide a detailed survey of related work in \sectionref{related}.

>>>>

\noindent\textbf{Other Related Work} 
Before ABY \cite{aby}, to improve efficiency, several works proposed
to mix secure computation protocols based on homomorphic
encryption with Yao’s garbled circuits protocol, e.g., \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}
  and developed tools that allowed writing a mixed SMC protocol, e.g., \cite{bogdanov,lone,tasty}. The assignment can
even be done automatically as was shown in \cite{autoS}. 
However, as noted by ABY, due to high conversion cost between homomorphic encryption and Yao's garbled circuit, these mixed protocols do not gain much over single protocol. Also, none of these works give a high-level developer-friendly language support.
No prior work has given a formal type system and operational semantics for mixed arithmetic and boolean back-ends.
In our evaluation, we use benchmarks for the problem of secure prediction where the cloud holds the secret model and the client holds the secret input. For this problem various works have considered tailor-made protocols depending on the model considered \cite{shafindss,wu,secureml,minionn}. In our evaluation, we compare our performance with these specialized protocols and give competitive run-times. We provide a detailed survey of related work in \sectionref{related}.
